Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-05 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items. Those represent different shades of gray of the  rectangle boxes. The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of Fig.~\ref{fig:flow}. The arrows, in the right side, it shows a point where some specific item is validated. The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux. At the end of the flow, all the items are defined and the sizing is finished.}

>>>>

\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items. Those represent different shades of gray of the  rectangle boxes. The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of Fig.~\ref{fig:flow}. The arrows, in the right side, it shows a point where some specific item is validated. The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux. The last rectangle box check the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from outlet; moreover, the inverter specified power must be lower than the charge controller power in order to avoid it to burn by overcharge. At the end of the flowchart, all the items are defined and the sizing is finished.}
